Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion

### 2023-07-31 Manuscript.Rmd
edits

---
title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
author: 
  - name : "Alexandra G. Mitchell"
    affiliation : "1"
  - name : "Jesper Fischer Ehmsen"
    affiliation : "1"
  - name : "Daniel Elmstrom Christensen"
    affiliation : "2"
  - name : "Anna Villaume Stuckert"
    affiliation : "3"
  - name : "Patrick Haggard"
    affiliation : "4"  
  - name : "Francesca Fardo"
    affiliation : "1"  
affiliation:
  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
  - id : "3"
    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
  - id : "4"
    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
  - id : "5"
    institution : "Danish Pain Research Center, Aarhus University, Denmark"
#date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document:
bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

The thermal grill illusion (TGI) is a perceptual phenomenon that challenges conventional understanding of pain perception.
It is a sensation of burning heat or pain when harmless cold and warm temperatures are applied to the skin simultaneously [@craig_thermal_1994; @craig_functional_1996].
Despite cold and warm temperatures being individually innocuous, their combination produces a contradictory burning sensation, even so the temperatures are insufficient to activate peripheral nociceptors.
The generation of this illusion is thus attributed to central nervous system mechanisms [@craig_thermal_1994; @fardo_beyond_2020].
Recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017].
However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.

@@

# Supplementary material
```{r,warning = F, message = F, echo = F}

>>>>

---
title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
author: 
  - name : "Alexandra G. Mitchell"
    affiliation : "1"
  - name : "Jesper Fischer Ehmsen"
    affiliation : "1"
  - name : "Daniel Elmstrom Christensen"
    affiliation : "1"
  - name : "Anna Villaume Stuckert"
    affiliation : "3"
  - name : "Patrick Haggard"
    affiliation : "4"  
  - name : "Francesca Fardo"
    affiliation : "1"  
affiliation:
  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
  - id : "3"
    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
  - id : "4"
    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
  - id : "5"
    institution : "Danish Pain Research Center, Aarhus University, Denmark"
#date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document:
bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

The thermal grill illusion (TGI) is a perceptual phenomenon that challenges conventional understanding of pain perception.
It is a sensation of burning heat or pain when harmless cold and warm temperatures are applied to the skin simultaneously [@craig_thermal_1994; @craig_functional_1996].
Despite cold and warm temperatures being individually innocuous, their combination produces a contradictory burning sensation, even so the temperatures are insufficient to activate peripheral nociceptors.
Thus researchers have attributed the generation of this illusion to complex mechanisms within the central nervous system [@craig_thermal_1994; @fardo_beyond_2020].
In particular, recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017].
However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.

@@

# Supplementary material

```{r,warning = F, message = F, echo = F}
